Machines are Among Us

### 2020-12-02 paper/main.tex
page number starts at 1 lol
added heatmap and some hyperparameter text

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

@@

We deconstructed a standard voting round of Among Us into three stages: 
communicationless information gain,
argument and debate, and the final vote. Building off of this, we decided 
to break our standard player model into a perception stage, 
communication stage, and voting stage. Each satge feeds into the next until the final
vote occurs to eliminate one of the models within the communicating group.
to simplify the game by both removing the tasks and killing and making the entire
\subsection{Modeling Interpretation and Communication}

@@

\subsection{Zero-sum Target}
The last stage is the most simple one, voting. The model simple takes the concetnated
hidden outputs from the communication stage and feeds them through
multi-layer perceptron layers. This finalizes as a player length probability vector
of a confidence that a specific player (at that index) should be voted out.

The "crew score" is the sum of all votes of any player for an imposter. The imposter loss
is the crew score, and the crew loss is the negation.
Relate back to GANs, zero-sum game so that adversarial works.
\subsection{Training Scheme}
There were multiple decisions we had to make when attempting to train the models.
Imposter/Crew two different models, multitude of different hyperparameters and
sizes of inputs/outputs.
\subsection{Challenges}
The main challenge in building and running the model
came mainly in the form of training time, gradient overlap, 
and hyperparameter search.

Another important challenge to recognize is the extreme "black box" architecture
of the model. With our current model iteration, we have no current approach to visualizing
exactly what the model is doing, especially with communication. Therefore there are
assumptions and estimations when creating conclusions about the model.

\section{Results}
% talk about our goal for a qualitatively "good" communication
% session.
\subsection{Oscillating Scores}
% talk about problems we saw frequently. show examples of "good" runs
% and bad runs
\subsection{Situation Hyperparameters}
% grid search results.
\subsection{Model Evolution}
% are the agents "improving" or just changing minorly to trick each other
\subsection{Interpreting Communcation Vectors}
\subsection{Future Directions}
This approach is just a start into understanding how neural networks
communicate with one another. Although assumptions can be made,
understanding the actual information being transferred between each model is
a dark area. Innovative techniques must be found to analyze this information flow 
in order to fully comprehend the strategy within the game.

>>>>

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}
\begin{document}

@@

@@

In order to examine the interactions between multiple agents -- some of who are
secretly imposters who must ``lie'', we chose to construct an ``Among Us''-esque scenario
for our models to partake in. On a high level, we wanted each agent to 
first collect information
independant of the others. Then, there should be some phase of communication between the
models -- qualitatively, it is during this stage that the agents will attempt to
deduce who the imposters are, an the imposters will attempt to blend in. Finally, the
agents all vote on who they think is a likely imposter. The upcoming sections
explain how we chose to model each of these phases in greater detail.
to simplify the ``game'' by both removing the tasks and killing and making the entire

Specifically, each agent is given as input a matrix consisting
of $N$ events. During each event, the agent ``sees'' some subset of the other players
(sight is reflexive and symmetric, but not transitive).
They also may experience a ``sabotage'', which means they are in the prescence
of an imposter who is sabotaging. They cannot see the imposter, but the imposter
can see them during this event. Ultimately, each agent will recieve
a $N \times (P + 1)$ matrix, where $P$ is the total number of players -- the first
$P$ values of a row indicate who the agent is seeing, and the final value indicates
a sabotage.

These event matrices are generated randomly using four key parameters: the total number
of players ($P$), the number of those players who are imposters ($I$), the chance that
any given pair of players will see one another during an event (view chance), and the 
chance that any given imposter will sabotage during an  event (sabotage chance).

\subsection{Modeling Interpretation and Communication}
In order to process the input events, our agent model has an LSTM, which
generates $c_N$ and $h_N$, which are used as the initial inputs
$h_0$ and $c_0$ to the next phase:
communication. Communcation is also modeled with an LSTM. During each ``round''
of communication, every agent contributes a message vector of size $M$ via
a small MLP using $h_t$ as input. These messages are collected into a matrix
of size $M \times P$, which is fed as input into each agent's LSTM so that
their memory can be updated before the next round of communication -- there
are $R$ rounds in total. We chose
to model communication this way because it is a simple and symmetric way for the agents
to pass information between each other in multiple rounds.

\subsection{Zero-sum Target}
The last stage is the most simple one -- voting. The model simple takes the $h_R$ and
$c_R$ from the end of the communication LSTM and feeds them through
a small MLP finalized with a softmax layer. This results in a probability vector
of a confidence that a specific player should be ``voted out''.

At the end of voting, we calculate a ``crew score''. This score is simply the
maximum vote-off score that any imposter recieved, where votes
are averaged across all agents. Clearly, the imposters would like to minimize the
votes on themselves, so their loss function for training purposes is
simply the crew score. Inversely, the crew's loss function is the negation of
the crew score. This takes the form of a zero-sum game with similar application
as in generative adversarial networks.
\subsection{Training Scheme}
There were multiple decisions we had to make when attempting to train the models.
Imposter/Crew two different models, multitude of different hyperparameters and
sizes of inputs/outputs.
\subsection{Challenges}
The main challenge in building and running the model
came mainly in the form of training time, gradient overlap, 
and hyperparameter search. As discussed previously, to help speed up training time
and reduce gradient overlap between multiple different models training over the
same dataset, we had to only train either one imposter or crew, and keep the rest constant.
This limits the quick adaptivity, and may lead to the models attempting to train
against the constant tcooperative models ratrher than against the adversarial model.

Furthermore, the immense number of combinations of hyperparameters
and input and outputs sizes, along with no precedent for recommended values,
lead us to generalize our model significantly. Although this may seem like an ability for
customizability, it severely reduces reproducability over small changes.

Another important challenge to recognize is the extreme "black box" architecture
of the model. With our current model iteration, we have no current approach to visualizing
exactly what the model is doing, especially with communication. Therefore there are
assumptions and estimations when creating conclusions about the model.
\subsection{Situation Hyperparameters}
To list the variable hyperparameters and input and outputs sizes for the player model,
overall, we have batch size, number of epochs, epoch length, the global LSTM hidden layer size, 
and the amount of players and imposters. For the perception phase, there is the
chance a player will view another player, the chance a sabotage occurs, and the number of $N$ events.  
The communication stage has variables the message size $M$ and the number of communication rounds
$R$.
\begin{figure*}
   \begin{center}
      \includegraphics[width=0.8 \textwidth]{img/grid_search.png}
   \end{center}
      \caption{A grid search heat map over the size parameters M (message vector) 
      and Rounds (the number of communications) displaying the ending Crew score after 6 epochs.
      }
   \label{fig:model}
\end{figure*}
\section{Results}
% talk about our goal for a qualitatively "good" communication
% session.
\subsection{Oscillating Scores}
% talk about problems we saw frequently. show examples of "good" runs
% and bad runs

% grid search results.
\subsection{Model Evolution}
% are the agents "improving" or just changing minorly to trick each other
\subsection{Interpreting Communcation Vectors}
\subsection{Future Directions}
This approach is just a start into understanding how neural networks
communicate with one another. Although assumptions can be made,
understanding the actual information being transferred between each model is
a dark area. Innovative techniques must be found to analyze this information flow 
in order to fully comprehend the strategy within the game.
